### 2024-04-16 paper/paper.qmd
Finished up modelling and introduction

---
title: "Cuisine and Yelp Ratings"
author: 
  - Moohaeng Sohn
thanks: "Code and data are available at: [https://github.com/alexsohn1126/yelp-analysis](https://github.com/alexsohn1126/yelp-analysis)"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(modelsummary)
library(arrow)
library(kableExtra)
library(here)
restaurants <- read_parquet(here("./data/analysis_data/restaurant_data.parquet"))
model <- readRDS(here("./models/restaurant_rating_model_logit.rds"))
```

# Introduction

Thanks to internet technology, we can get hundreds, if not thousands of reviews of restaurants around us. This means we can choose which restaurants we will go to based on those reviews. Therefore, keeping a high review rating is very important for a restaurant's long-term success.

Yelp is a website where people can post reviews about local businesses, containing 287 million reviews [@yelpfacts]. Yelp's reviews are based on the 5-star system. Users can choose between one to five stars to put on their review. These reviews are collected and averaged, which becomes the rating for the establishment. We will use a dataset from Yelp which we will dive into in @sec-data.

TODO: ADD THINGS ABOUT WHAT WE FOUND OUT AND WHY IS IT IMPORTANT

In this paper, our estimand of interest is how different factors such as the cuisine of the restaurant, or the price of the menu items in the restaurants affect the rating of a restaurant. We will first explore the dataset in @sec-data, and discuss the model the relationship between aforementioned variables using logistic regression in #sec-model. Then we will look at the results in @sec-res, finally discussing about these results in @sec-discussion.

# Data {#sec-data}

The restaurant review dataset we will use is from Yelp. Yelp offers an academic dataset for the public to use, although it is a small subset of their massive database [@yelpdataset-faq]. It only contains

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

modelsummary(list("my model" = model))

modelplot(model, conf_level = 0.9) +
  labs(x = "90 per cent credibility interval")
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model {#sec-model}

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results {#sec-res}

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion {#sec-discussion}

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-04-16 scripts/00-simulate_data.R

@@ -21,8 +21,8 @@ restaurants <- tibble(
   restaurant_name = paste("Restaurant", seq(1:num_restaurants)),
   # Generating random float ratings between 1 and 5
   rating = runif(num_restaurants, min = 1, max = 5),
-  # Sample from a selection of categories
-  category = sample(c("Italian", "Mexican", "Indian", "Chinese"), num_restaurants, replace = TRUE)
+  # Sample from a selection of cuisines
+  cuisine = sample(c("Italian", "Mexican", "Indian", "Chinese", "Other"), num_restaurants, replace = TRUE)
 )
 
 #### Test data ####
@@ -30,7 +30,7 @@ restaurants <- tibble(
 # Test column types
 is.character(restaurants$restaurant_name)
 is.numeric(restaurants$rating) 
-is.character(restaurants$category)
+is.character(restaurants$cuisine)
 
 # Test rating bounds
 # All ratings must be between 1 to 5 (no 0 stars for a review, nor 6+ stars)
@@ -38,4 +38,4 @@ all(restaurants$rating >= 1)
 all(restaurants$rating <= 5)
 
 # Test that categories are types of cuisines that we specified
-all(is.element(restaurants$category, c("Italian", "Mexican", "Indian", "Chinese")))
+all(is.element(restaurants$cuisine, c("Italian", "Mexican", "Indian", "Chinese", "Other")))

### 2024-04-16 scripts/02-data_cleaning.R

@@ -27,11 +27,16 @@ business <- business |>
 cuisines <- c("American", "Mexican", "Italian", "Chinese", "Japanese", "Mediterranean", "Thai", "Vietnamese", "Indian", "Caribbean", "Middle Eastern", "French")
 cuisines_business <- business |>
   mutate(cuisine = case_when(
+    # If any of the cuisines in the category, categorize them as that cuisine
     str_detect(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)) ~ 
       str_extract(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)),
+    # If not, put them as Other
     TRUE ~ "Other"
-  )) |>
-  select(restaurant_name=name, rating=stars, cuisine, price=attributes.RestaurantsPriceRange2)
+  ),
+  price = as.numeric(attributes.RestaurantsPriceRange2)) |>
+  # Filter out no category restaurants
+  filter(!is.na(attributes.RestaurantsPriceRange2)) |>
+  select(restaurant_name=name, rating=stars, cuisine, price)
 
 #### Save data ####
 write_parquet(cuisines_business, "./data/analysis_data/restaurant_data.parquet")

### 2024-04-16 scripts/03-test_data.R

@@ -1,15 +1,31 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests cleaned yelp restaurants data
+# Author: Moohaeng Sohn
+# Date: 16 April 2024
+# Contact: alex.sohn@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Run 02-data_cleaning.R
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(arrow)
+
+#### Load Data ####
+restaurants <- read_parquet("./data/analysis_data/restaurant_data.parquet")
 
 #### Test data ####
+# Test column types
+is.character(restaurants$restaurant_name)
+is.numeric(restaurants$rating) 
+is.character(restaurants$cuisine)
+
+# Test rating bounds
+# All ratings must be between 1 to 5 (no 0 stars for a review, nor 6+ stars)
+all(restaurants$rating >= 1)
+all(restaurants$rating <= 5)
+
+# Test that categories are types of cuisines that we specified
+cuisines <- c("American", "Mexican", "Italian", "Chinese", "Japanese", "Mediterranean", "Thai", "Vietnamese", "Indian", "Caribbean", "Middle Eastern", "French", "Other")
+all(is.element(restaurants$cuisine, cuisines))
+

### 2024-04-16 scripts/04-model.R

@@ -1,37 +1,44 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models whether the review is positive based on multiple variables
+# Author: Moohaeng Sohn
+# Date: 16 April 2024
+# Contact: alex.sohn@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Run 02-data_cleaning.R
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+restaurants <- read_parquet("./data/analysis_data/restaurant_data.parquet")
 
 ### Model data ####
+# Convert 5-star rating into Good/bad restaurant
+threshold = median(restaurants$rating)
+
+restaurants <- restaurants |>
+  mutate(mostly_positive = case_when(
+    rating <= threshold ~ 0,
+    TRUE ~ 1
+  ))
+
 first_model <-
   stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
+    formula = mostly_positive ~ cuisine + price,
+    data = restaurants,
+    family = binomial(link="logit"),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 853
   )
-
 
 #### Save model ####
 saveRDS(
   first_model,
-  file = "models/first_model.rds"
+  file = "models/restaurant_rating_model_logit2.rds"
 )
 
 

### 2024-04-17 paper/paper.qmd
Working on Data section

@@
 number-sections: true
+toc: true
 bibliography: references.bib
@@
 library(here)
+library(rstanarm)
 restaurants <- read_parquet(here("./data/analysis_data/restaurant_data.parquet"))
@@
 In this paper, our estimand of interest is how different factors such as the cuisine of the restaurant, or the price of the menu items in the restaurants affect the rating of a restaurant.
-We will first explore the dataset in @sec-data, and discuss the model the relationship between aforementioned variables using logistic regression in #sec-model.
+We will first explore the dataset in @sec-data, and discuss the model the relationship between aforementioned variables using logistic regression in @sec-model.
 Then we will look at the results in @sec-res, finally discussing about these results in @sec-discussion.
+
+We used the programming language R [@citeR], along with packages `tidyverse` [@tidyverse], `rstanarm` [@rstanarm], `jsonlite` [@jsonlite], `arrow` [@arrow], `modelsummary` [@modelsummary], `kableExtra` [@kableExtra], `here` [@here].
 
@@
 Yelp offers an academic dataset for the public to use, although it is a small subset of their massive database [@yelpdataset-faq].
-It only contains
+The dataset is split between multiple JSON files, but we will only focus on businesses JSON.
+The raw businesses dataset contains 150,346 businesses.
+These businesses are from metropolitan areas in United States and Canada.
+Specifically, from metropolitan areas near Montreal, Calgary, Toronto, Pittsburgh, Charlotte, Urbana-Champaign, Phoenix, Las Vegas, Madison, and Cleveland [@yelpdataset-faq].
+
+Another possible source of restaurant reviews could have been from Google reviews of restaurants, but that requires us to use Google Business Profile APIs, which cost money.
+There is always an option to perform webscraping, but this is a gray area legally, and may be computationally expensive.
+There are other review websites such as TripAdvisor, but they do not seem to have a dataset open to the public like Yelp does.
+
+The dataset contains multiple variables such as the name of the business, the location of the business, and things such as amenities on site.
+We have filtered through the raw dataset to only contain restaurants.
+There were a total of 47,231 restaurants in the final dataset.
+We will focus on the star rating, categories, and price range of the menu in the restaurant.
+
+## Star Rating
+
+Star rating is the average star rating of a restaurant.
+One odd thing about the star rating given in the dataset is that it is rounded to the nearest star or half of a star.
+So all possible values of star ratings are: 1.0, 1.5, 2.0, and so on until 5.0.
+Notice that the minimum star rating is one and the maximum star rating is five.
+This is because the minimum star rating that someone can give a restaurant is 1 stars, and the maximum star rating is 5 stars.
+While the average star rating can have 0.5 star increments, users' reviews can only give ratings in 1 star increments.
+For example, no 4.5 stars can be given in a review.
+Each user can rate a business only once, though they are free to change their rating later, one user cannot post multiple reviews about a restaurant.
+This limits the power each user has to change the rating of a business.
+
+Yelp has removed businesses that had 3 or less reviews posted that were older than 14 days at the date of collection in the dataset [@yelpdataset-faq].
+This means restaurants that just opened, or didn't have enough reviews at the time of data collection would not have been included in this dataset.
+
+@Fig-star-rating-distribution shows us that 4.0 is the most common star rating of restaurants.
+This distribution is left skewed, as we can see the rating gradually increases from 1.0 to 4.0, then quickly drops off from 4.0 to 5.0.
+We can infer from this that most people consider somewhere around 4-stars an average dining experience.
+
+```{r}
+#| label: fig-star-rating-distribution
+#| fig-cap: Distribution of Star Ratings
+#| echo: false
+
+restaurants %>%
+  ggplot(aes(x = rating)) +
+  geom_histogram(binwidth = 0.25, fill = "grey", color = "black") +
+  labs(title = "Distribution of Star Ratings",
+       x = "Stars",
+       y = "Frequency") +
+  theme_minimal()
+```
+
+```{r}
+#| label: tbl-star-rating-summary
+#| tbl-cap: "Summary Statistics of Star Ratings"
+#| echo: false
+
+summary_stats <- restaurants %>%
+  summarize(
+    Count = n(),
+    Mean = mean(rating),
+    Median = median(rating),
+    SD = sd(rating),
+    Minimum = min(rating),
+    Maximum = max(rating)
+  )
+
+# Create a table using kable
+summary_table <- kable(summary_stats)
+
+summary_table
+```
+
+## Categories (Cuisine)
+
+Categories for a restaurant describes what kind of business it is.
+These categories are chosen manually by the business owners [@yelpcategory].
+Because Yelp is a business review platform, we have decided to filter out non-restaurant businesses from our final dataset.
+This meant any restaurants which didn't include one of the categories: "Restaurants", "Food", "Fast Food" would not be included in the final dataset.
+After filtering out non-restaurants, we have chosen top 12 cuisines to categorize each restaurant into.
+The restaurants that did not have these cuisines in their categories were put into "Other" category.
+This is why we have named this section also cuisine, as we will focus on cuisine categories of restaurants.
+
+```{r}
+#| label: tbl-category-summary
+#| tbl-cap: "Numbers of Restaurants Per Cuisine"
+#| echo: false
+
+# Calculate the count of restaurants per category
+restaurant_summary <- restaurants %>%
+  group_by(cuisine) %>%
+  summarize(restaurants_count = n()) %>%
+  ungroup()
+
+# Calculate the percentage of restaurants per category
+total_restaurants <- nrow(restaurants)
+restaurant_summary <- restaurant_summary %>%
+  mutate(percentage = round((restaurants_count / total_restaurants) * 100, 2))
+
+# Arrange the result by frequency in descending order
+restaurant_summary <- restaurant_summary %>%
+  arrange(desc(restaurants_count))
+
+# Rename the columns
+colnames(restaurant_summary) <- c("Cuisine", "Number of Restaurants", "Percentage (%)")
+
+# Print table
+kable(restaurant_summary)
+```
+
+## Price Range
 
@@
 #| echo: false
-
-modelsummary(list("my model" = model))
-
-modelplot(model, conf_level = 0.9) +
-  labs(x = "90 per cent credibility interval")
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
 #| warning: false
@@
 
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
+data_counts <- restaurants %>%
+  group_by(cuisine, price) %>%
+  summarize(count = n()) %>%
+  ungroup()
 
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
+# Calculate the total count of each cuisine category
+cuisine_total_counts <- data_counts %>%
+  group_by(cuisine) %>%
+  summarize(total_count = sum(count))
+
+# Merge the counts with the total counts
+data_normalized <- data_counts %>%
+  left_join(cuisine_total_counts, by = "cuisine") %>%
+  mutate(normalized_count = count / total_count)
+
+# Plot the relationship between cuisine and price range with normalized counts
+data_normalized %>%
+  ggplot(aes(x = cuisine, y = normalized_count, fill = factor(price))) +
+  geom_bar(stat = "identity") +
+  labs(title = "Relationship between Cuisine and Price Range (Normalized)",
+       x = "Cuisine",
+       y = "Percentage",
+       fill = "Price Range") +
   theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 ```
-
-Talk way more about it.
 
@@
 
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
 ```
@@
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
 ```
@@
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
 ```

### 2024-04-18 paper/paper.qmd
Push paper related things before quarto god gets mad at me again and pulls me through unrelenting hell of latex errors

@@
 library(rstanarm)
-restaurants <- read_parquet(here("./data/analysis_data/restaurant_data.parquet"))
-model <- readRDS(here("./models/restaurant_rating_model_logit.rds"))
+data <- read_parquet(here("./data/analysis_data/restaurant_data.parquet"))
+model <- readRDS(here("./models/restaurant_rating_model_ord_logit.rds"))
 ```
@@
 We have filtered through the raw dataset to only contain restaurants.
-There were a total of 47,231 restaurants in the final dataset.
+There were a total of 47,213 restaurants in the final dataset.
 We will focus on the star rating, categories, and price range of the menu in the restaurant.
@@
 So all possible values of star ratings are: 1.0, 1.5, 2.0, and so on until 5.0.
-Notice that the minimum star rating is one and the maximum star rating is five.
-This is because the minimum star rating that someone can give a restaurant is 1 stars, and the maximum star rating is 5 stars.
-While the average star rating can have 0.5 star increments, users' reviews can only give ratings in 1 star increments.
-For example, no 4.5 stars can be given in a review.
-Each user can rate a business only once, though they are free to change their rating later, one user cannot post multiple reviews about a restaurant.
-This limits the power each user has to change the rating of a business.
-
-Yelp has removed businesses that had 3 or less reviews posted that were older than 14 days at the date of collection in the dataset [@yelpdataset-faq].
-This means restaurants that just opened, or didn't have enough reviews at the time of data collection would not have been included in this dataset.
 
@@
 We can infer from this that most people consider somewhere around 4-stars an average dining experience.
+
+@Tbl-star-rating-summary shows the summary statistics of star ratings, and we can see that as we explained, that the minimum is 1.0 and the maximum is 5.0.
+The standard deviation isn't that big, which is to be expected because most of the restaurants lie between 3.5 to 4.5 rating range.
 
@@
 
-restaurants %>%
+data %>%
   ggplot(aes(x = rating)) +
@@
 
-summary_stats <- restaurants %>%
+summary_stats <- data %>%
   summarize(
@@
 
+@Tbl-category-summary shows us what types of cuisines we have selected, and the number of restaurants with that cuisine in their category.
+We can see nearly half of the restaurants are categorized as "Other".
+The next largest cuisine in our dataset is American.
+This may be due to the fact that all the restaurants in the dataset are from United States and Canada.
+
 ```{r}
@@
 # Calculate the count of restaurants per category
-restaurant_summary <- restaurants %>%
+restaurant_summary <- data %>%
   group_by(cuisine) %>%
@@
 # Calculate the percentage of restaurants per category
-total_restaurants <- nrow(restaurants)
+total_restaurants <- nrow(data)
 restaurant_summary <- restaurant_summary %>%
@@
 
+The price range is given as an integer from 1 to 4, inclusive.
+This is supposed to indicate how expensive the restaurant is per person.
+1 being more affordable, and 4 being more expensive.
+There were restaurants with no price ranges, and those were discarded from the cleaned dataset.
+On Yelp's website, these price ranges are shown as number of dollar signs equal to the price range.
+For example, Yelp would show one dollar sign if price range is 1.
+
+@Tbl-price-range-summary shows that the over 95% of the restaurants have price range of 1 or 2.
+About 95.81% of restaurants in the database are in price range 1 or 2.
+Only 3.73% of the restaurants are in price range 3, and even less, 0.46% of the restaurants are in price range 4.
+
+```{r}
+#| label: tbl-price-range-summary
+#| tbl-cap: "Numbers of Restaurants Per Price Range"
+#| echo: false
+
+# Calculate the count of restaurants per category
+restaurant_summary <- data %>%
+  group_by(price) %>%
+  summarize(restaurants_count = n()) %>%
+  ungroup()
+
+# Calculate the percentage of restaurants per category
+total_restaurants <- nrow(data)
+restaurant_summary <- restaurant_summary %>%
+  mutate(percentage = round((restaurants_count / total_restaurants) * 100, 2))
+
+# Arrange the result by frequency in descending order
+restaurant_summary <- restaurant_summary %>%
+  arrange(price)
+
+# Rename the columns
+colnames(restaurant_summary) <- c("Price Range", "Number of Restaurants", "Percentage (%)")
+
+# Print table
+kable(restaurant_summary)
+```
+
+## Measurement
+
+For star ratings, the minimum star rating is one and the maximum star rating is five.
+This is because the minimum star rating that someone can give a restaurant is 1 stars, and the maximum star rating is 5 stars.
+While the average star rating can have 0.5 star increments, users' reviews can only give ratings in 1 star increments.
+For example, no 4.5 stars can be given in a review.
+Each user can rate a business only once, though they are free to change their rating later, one user cannot post multiple reviews about a restaurant.
+This limits the power each user has to change the rating of a business.
+
+As mentioned above, categories for a restaurant is not given automatically, rather given by the business owners.
+This means it can be a bit inaccurate when it comes to what exact cuisine that a restaurant serves.
+Another way the cuisines can be inaccurate is when a restaurant serves foods from multiple cuisines.
+This makes it complicated to categorize them exactly into each cuisine.
+
+The exact method of how the price range was decided by Yelp is not known.
+We can make guesses about what kind of information they use to determine the price range, but no clear documentation is available for the price range statistics.
+We were able to find online discussions about the price range being decided by the check-in feature of Yelp, possibly implying that there are certain price ranges that Yelp uses to display these price ranges [@yelppricedef].
+
+# Model {#sec-model}
+
+We are trying to model the rating $y$, and as we have discussed in the data section, there are only 9 possible outcomes.
+From 1.0, to 5.0, in increments of 0.5.
+Therefore we will use ordinal logistic regression.
+If we assume that the observed rating $y$ is from a continuous variable $y^*$, then we can say that:
+
+$$
+y = \begin{cases}
+1.0 & \text{ if } y^* \leq c_{1.0|1.5} \\
+1.5 & \text{ if } y^* \in (c_{1.0|1.5}, c_{1.5|2.0}) \\
+\vdots & \\
+4.5 & \text{ if } y^* \in (c_{4.0|4.5}, c_{4.5|5.0}) \\
+5.0 & \text{ if } y^* \geq c_{4.5|5.0}
+\end{cases}
+$$
+
+Where $c_{n_1|n_2}$ represents the cutoff between $n_1$ rating and $n_2$ rating. The above notations are borrowed from @regandothers \[p.276\] and @evalLLM [p.12].
+
+We will use a Bayesian framework to make our model. To do this, we use `rstanarm` [@rstanarm] R package. Background details and diagnostics are included in [Appendix -@sec-model-details].
+
+## Model set-up
+
+We will model the final discrete rating $y$ by a continuous variable $y^*$. Because we are doing ordinal logistic regression, $y^*$ will have a logistic distribution.
+
+$$
+y^* = \beta_1 \cdot \text{cuisine}_i + \beta_2 \cdot \text{price}_i
+$$
+
+We use the R2 prior, because `rstanarm` requires us to do this for this computational process, with the mean set as 0.3 as suggested by @regandothers [p.276].
+R2 uses the prior beliefs about the location about $R^2$, which is "the proportion of variance in the outcome attributable to the predictors" @rstanarm.
+We use default priors from `rstanarm` for the cut points ($c_{n_1|n_2}$), which is a dirichlet distribution with concentration of 1.
+
+### Model justification
+
+We can expect that if a restaurant has higher prices, then the restaurant will be higher quality.
+This should be reflected in the ratings by the customers, and those restaurants with higher quality will have higher ratings.
+However, one could set much higher expectations for more expensive restaurants, effectively cancelling out the higher quality food and service that is expected from a higher priced restaurant.
+We will keep this in mind when we discuss our results.
+
+We also expect that different cuisines will have different ratings.
+This dataset is exclusively about restaurants in North America.
+Therefore we may expect that reviewers are more likely to be from North America, so perhaps they would give a higher rating to a restaurant that serves western cuisine, such as Italian, or American.
+
+# Results {#sec-res}
+
+Our results are summarized in @tbl-modelresults, and @fig-modelresults.
+
+The rows with numbers and a vertical line between them are the cutpoints. For example, a rating would be considered 1.5 if we had a $y^*$ that is greater than $1.0|1.5$ and less than $1.5|2.0$.
+
+We can see that nearly all cuisines has a positive effect on the rating, except for Chinese.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+
+#modelsummary(list("my model" = model))
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: fig-modelresults
+#| fig-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+
+#modelplot(model, conf_level = 0.9) +
+ # labs(x = "90% credibility interval")
+```
+
+# Discussion {#sec-discussion}
+
+## First discussion point {#sec-first-point}
+
 ```{r}
@@
 
-data_counts <- restaurants %>%
+data_counts <- data %>%
   group_by(cuisine, price) %>%
@@
 
-# Model {#sec-model}
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results {#sec-res}
-
-Our results are summarized in @tbl-modelresults.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-```
-
-# Discussion {#sec-discussion}
-
-## First discussion point {#sec-first-point}
-
 If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
@@
 
-# Appendix {-}
-
-# Additional data details
+# Appendix {.unnumbered}
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows that the there is a large disparity between the predictions and the actual data.
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows the posteriors are around where the credible intervals are in priors.
 
@@
 #| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+#| label: fig-ppcheckandposteriorvsprior-1
+#| fig-height: 7
+#| fig-cap: "Examining how the model fits, and is affected by the data - Posterior prediction check"
 
+pp_plot <- pp_check(model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+pp_plot
+
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheckandposteriorvsprior-2
+#| fig-height: 7
+#| fig-cap: "Examining how the model fits, and is affected by the data - Comparing the posterior with the prior"
+
+pvpplot <- posterior_vs_prior(model) +
+  theme_minimal() +
+  theme(legend.position = "bottom") +
+  coord_flip()
+
+pvpplot
 ```
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+@fig-stanareyouokay-1 is a trace plot. It shows the chains cover a constant amount of region. This suggests that a large amount of sample is chosen at around the target space we want to explore.
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+@fig-stanareyouokay-2 is a Rhat plot. It shows all of the Rhat values are very close to 1, meaning the chains had enough time to converge.
 
@@
 #| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
+#| label: fig-stanareyouokay-1
+#| fig-height: 7
+#| fig-cap: "Checking the convergence of the MCMC algorithm - Trace Plot"
+
+plot(model, "trace") +
+    theme(legend.position = "bottom")
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-stanareyouokay-2
+#| fig-height: 7
+#| fig-cap: "Checking the convergence of the MCMC algorithm - Rhat Plot"
+
+plot(model, "rhat") +
+  theme_minimal() +
+  theme(legend.position = "bottom")
 

### 2024-04-18 scripts/02-data_cleaning.R

@@ -26,6 +26,8 @@ business <- business |>
 # This list of cuisine is based on the Yelp dataset's categories 
 cuisines <- c("American", "Mexican", "Italian", "Chinese", "Japanese", "Mediterranean", "Thai", "Vietnamese", "Indian", "Caribbean", "Middle Eastern", "French")
 cuisines_business <- business |>
+  # Filter out none category restaurants
+  filter(!is.na(attributes.RestaurantsPriceRange2), attributes.RestaurantsPriceRange2 != "None") |>
   mutate(cuisine = case_when(
     # If any of the cuisines in the category, categorize them as that cuisine
     str_detect(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)) ~ 
@@ -34,8 +36,6 @@ cuisines_business <- business |>
     TRUE ~ "Other"
   ),
   price = as.numeric(attributes.RestaurantsPriceRange2)) |>
-  # Filter out no category restaurants
-  filter(!is.na(attributes.RestaurantsPriceRange2)) |>
   select(restaurant_name=name, rating=stars, cuisine, price)
 
 #### Save data ####

### 2024-04-18 scripts/04-model.R

@@ -13,32 +13,29 @@ library(rstanarm)
 library(arrow)
 
 #### Read data ####
-restaurants <- read_parquet("./data/analysis_data/restaurant_data.parquet")
+data <- read_parquet("./data/analysis_data/restaurant_data.parquet")
 
 ### Model data ####
-# Convert 5-star rating into Good/bad restaurant
-threshold = median(restaurants$rating)
 
-restaurants <- restaurants |>
-  mutate(mostly_positive = case_when(
-    rating <= threshold ~ 0,
-    TRUE ~ 1
-  ))
+# Rough model
+# Don't import the whole MASS library as it interferes with select() from tidyverse
+#rough_model <-
+#  MASS::polr(factor(rating) ~ cuisine + factor(price), data = data)
 
-first_model <-
-  stan_glm(
-    formula = mostly_positive ~ cuisine + price,
-    data = restaurants,
-    family = binomial(link="logit"),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 853
+# uses 6 cores, reduce if necessary
+model <-
+  stan_polr(
+    formula = factor(rating) ~ cuisine + factor(price),
+    cores = 6,
+    data = data,
+    prior = R2(0.3, "mean"),
+    seed = 302
   )
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/restaurant_rating_model_logit2.rds"
+  model,
+  file = "models/restaurant_rating_model_ord_logit.rds"
 )
 
 

### 2024-04-19 paper/paper.qmd
Finish up paper, add map feature in

@@
 ---
-title: "Cuisine and Yelp Ratings"
+title: "Modelling the Yelp Rating of Restaurants: Disparity of Rating Between Restaurant Cuisines and Prices"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "We use the Yelp dataset to explore and model how different attributes of a restaurant play a factor in the review ratings.
+We found there are some variables which are promising predictors for the rating of a restaurant.
+Cuisines such as Chinese or Mexican tended to have lower ratings, and lower priced cuisines performed worse.
+This study can be used to predict whether a restaurant will be successful or not."
 format: pdf
@@
 
-TODO: ADD THINGS ABOUT WHAT WE FOUND OUT AND WHY IS IT IMPORTANT
-
 In this paper, our estimand of interest is how different factors such as the cuisine of the restaurant, or the price of the menu items in the restaurants affect the rating of a restaurant.
@@
 
-We used the programming language R [@citeR], along with packages `tidyverse` [@tidyverse], `rstanarm` [@rstanarm], `jsonlite` [@jsonlite], `arrow` [@arrow], `modelsummary` [@modelsummary], `kableExtra` [@kableExtra], `here` [@here].
+We found out that higher the price of a restaurant, more likely it will have a higher rating, though with a couple of exceptions.
+And certain cuisines performed significantly worse than other cuisines.
+We discuss why that may be the case using graphs and tables in @sec-discussion.
+This study may be important to entrepreneurs whom may be interested in how these reviews may possibly be biased due to the cuisine and the price of a restaurant.
+
+We used the programming language R [@citeR], along with packages `tidyverse` [@tidyverse], `rstanarm` [@rstanarm], `jsonlite` [@jsonlite], `arrow` [@arrow], `modelsummary` [@modelsummary], `kableExtra` [@kableExtra], `here` [@here], `leaflet` [@leaflet], `htmlwidgets` [@htmlwidgets].
 
@@
 The raw businesses dataset contains 150,346 businesses.
+
 These businesses are from metropolitan areas in United States and Canada.
-Specifically, from metropolitan areas near Montreal, Calgary, Toronto, Pittsburgh, Charlotte, Urbana-Champaign, Phoenix, Las Vegas, Madison, and Cleveland [@yelpdataset-faq].
+Yelp claims these restaurants are from metropolitan areas near Montreal, Calgary, Toronto, Pittsburgh, Charlotte, Urbana-Champaign, Phoenix, Las Vegas, Madison, and Cleveland [@yelpdataset-faq].
+But if you map out the raw dataset as we did in @sec-dataset-map, you will see that there are no restaurants from cities such as Toronto or Montreal or Calgary.
+This is an error on Yelp's data documentation, but we won't be dealing with locations of restaurants directly, so we won't be heavily affected by this error.
 
@@
 
-data %>%
+data |>
   ggplot(aes(x = rating)) +
@@
 
-summary_stats <- data %>%
+summary_stats <- data |>
   summarize(
@@
 # Calculate the count of restaurants per category
-restaurant_summary <- data %>%
-  group_by(cuisine) %>%
-  summarize(restaurants_count = n()) %>%
+restaurant_summary <- data |>
+  group_by(cuisine) |>
+  summarize(restaurants_count = n()) |>
   ungroup()
@@
 total_restaurants <- nrow(data)
-restaurant_summary <- restaurant_summary %>%
+restaurant_summary <- restaurant_summary |>
   mutate(percentage = round((restaurants_count / total_restaurants) * 100, 2))
@@
 # Arrange the result by frequency in descending order
-restaurant_summary <- restaurant_summary %>%
+restaurant_summary <- restaurant_summary |>
   arrange(desc(restaurants_count))
@@
 # Calculate the count of restaurants per category
-restaurant_summary <- data %>%
-  group_by(price) %>%
-  summarize(restaurants_count = n()) %>%
+restaurant_summary <- data |>
+  group_by(price) |>
+  summarize(restaurants_count = n()) |>
   ungroup()
@@
 # Arrange the result by frequency in descending order
-restaurant_summary <- restaurant_summary %>%
+restaurant_summary <- restaurant_summary |>
   arrange(price)
@@
 
-The exact method of how the price range was decided by Yelp is not known.
-We can make guesses about what kind of information they use to determine the price range, but no clear documentation is available for the price range statistics.
-We were able to find online discussions about the price range being decided by the check-in feature of Yelp, possibly implying that there are certain price ranges that Yelp uses to display these price ranges [@yelppricedef].
+Yelp decides the price of the restaurant by crowdsourcing the price of the restaurant [@Yu_Margolin_2021].
+According to @Yu_Margolin_2021, the price range of the restaurant is decided by the price brackets as shown in @tbl-prices.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-prices
+#| tbl-cap: "Table of how Yelp Maps Price Ranges"
+#| warning: false
+
+# Make a tibble of prices, and its corresponding value in our dataset
+tableData <- tibble(
+  price_range_num = 1:4,
+  price_brackets = c("Under $10", "$11 - $30", "$31 - $60", "Over $61")
+)
+
+# Print table
+kable(tableData, align = c("c", "c"), col.names = c("Price Range Number", "Price"))
+```
 
@@
 
-We can see that nearly all cuisines has a positive effect on the rating, except for Chinese.
+One thing to note is that `rstanarm` takes the first factor from increasing lexicographic order and sets it as a default.
+So you won't see American cuisine nor price range of 1 in @tbl-modelresults and @fig-modelresults.
+So every coefficient listed here is how different cuisines/price ranges perform *compared to* American cuisine and price range of 1.
+
+With that in mind, let's explore how different cuisines perform compared to American cuisine.
+Most cuisines are likely to increase the rating of a restaurant.
+However, according to our model, if a restaurant serves Chinese cuisine, it will receive a slightly lower rating than American restaurants.
+Also, a restaurant serving Italian or Mexican cuisines will receive roughly the same rating, as that of an American restaurant.
+Rest of the cuisines perform better than American cuisine.
+
+And as for price ranges, we can see compared to restaurants with price range of 1, those with price range 2 gets significantly higher rating.
+The increase of rating from going from price range of 1 to 2 is larger than that of 2 to 3, and that is larger still than that of 3 to 4.
+In other words, we have diminishing returns as the price range increases on the rating of the restaurant.
 
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| tbl-cap: "Table of how different cuisines and price range affects the rating of a restaurant"
 #| warning: false
 
-#modelsummary(list("my model" = model))
+modelsummary(list("Coefficients and Cutpoints" = model))
 ```
@@
 #| label: fig-modelresults
-#| fig-cap: "Explanatory models of flight time based on wing width and wing length"
+#| fig-cap: "Exploring The effects of cuisines and price ranges on the rating of a Restaurant"
 #| warning: false
 
-#modelplot(model, conf_level = 0.9) +
- # labs(x = "90% credibility interval")
+modelplot(model, conf_level = 0.9) +
+ labs(x = "Coefficient Estimates and Their 90% Credible Intervals")
 ```
@@
 
-## First discussion point {#sec-first-point}
+## Rating Disparity Between Cuisines {#sec-first-point}
+
+Certain cuisines had worse effect on restaurant rating than others.
+Namely, Chinese, American, Italian, and Mexican cuisines had noticeably worse rating than others.
+While it is plausible to state that restaurants with certain cuisines are simply worse, we will try to explain this backed with research.
+
+As for Chinese cuisine, one possible cause is the stigma around Chinese food.
+Chinese restaurant syndrome was a list of symptoms supposedly linked by Chinese restaurants' excessive usage of monosodium glutamate (MSG) [@Mekkodathil_Sathian_2017].
+Dr.
+Robert Ho Man Kwok first coined the term "Chinese Restaurant Syndrome" back in April of 1968, sending a letter to the New England Journal of Medicine [@LeMesurier_2017].
+This stigma against Chinese restaurants could still be remaining today, leading to a lower rating.
+
+American, Italian, and Mexican cuisine's bad performance could be explained by the demographic of the restaurants.
+All the restaurants in the dataset are in United States and Canada.
+All 3 aforementioned cuisines have very close ties with these countries.
+American cuisine is from United States.
+Italian cuisine is from Italy, but a lot of Italians are living in North America.
+Around 16 million Italian descendants are living in United States [@USCensus], and 1.5 million in Canada [@canadaCensus].
+Mexico shares a border with United states, therefore a ton of cultural influences were made in southern United States by Mexicans.
+What we propose is that people rate restaurants that serve foods from their own culture harshly.
+For example, people who have Mexican parents or has been raised with Mexican culture will have higher standards for Mexican food.
+
+We can try attributing this to the fact that different cuisines will have different price ranges.
+Therefore one can argue that those cuisines with higher proportion of low price restaurants will be more likely to have lower ratings.
+@Fig-cuisine-price-rel shows each cuisine's price range proportions.
+It shows that while Chinese and Mexican restaurants have high proportion of restaurants with price range of 1, but it is not the case for American and Italian cuisine.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: fig-cuisine-price-rel
+#| fig-cap: "Relationship between Cuisine and Price Range (Normalized)"
 #| echo: false
@@
 
-data_counts <- data %>%
-  group_by(cuisine, price) %>%
-  summarize(count = n()) %>%
+data_counts <- data |>
+  group_by(cuisine, price) |>
+  summarize(count = n()) |>
   ungroup()
@@
 # Calculate the total count of each cuisine category
-cuisine_total_counts <- data_counts %>%
-  group_by(cuisine) %>%
+cuisine_total_counts <- data_counts |>
+  group_by(cuisine) |>
   summarize(total_count = sum(count))
@@
 # Merge the counts with the total counts
-data_normalized <- data_counts %>%
-  left_join(cuisine_total_counts, by = "cuisine") %>%
-  mutate(normalized_count = count / total_count)
+data_normalized <- data_counts |>
+  left_join(cuisine_total_counts, by = "cuisine") |>
+  mutate(normalized_count = count / total_count) |>
+  arrange(count)
 
 # Plot the relationship between cuisine and price range with normalized counts
-data_normalized %>%
+data_normalized |>
   ggplot(aes(x = cuisine, y = normalized_count, fill = factor(price))) +
   geom_bar(stat = "identity") +
-  labs(title = "Relationship between Cuisine and Price Range (Normalized)",
-       x = "Cuisine",
+  labs(x = "Cuisine",
        y = "Percentage",
@@
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+Another interesting insight is that these 4 cuisines we have listed as "worse" than others are the top 4 cuisines excluding "Other" category in our dataset (Check @tbl-category-summary).
+Perhaps more restaurants there are for certain cuisines, people's expectations are higher, leading to lower rating for "average" experiences in those restaurants.
+@Fig-cuisine-ratings shows the relationship between the number of restaurant and the rating that a cuisine has.
+We can clearly see there is a downward trend as number of restaurants increase.
+This could have occurred because people associate rare cuisine as being better.
+Also, there is a possibility that the owners that would care about their Yelp categories are also more likely to care about the service and the food of the restaurant.
 
-## Second discussion point
+```{r}
+#| label: fig-cuisine-ratings
+#| fig-cap: "Average Rating vs. Number of Restaurants by Cuisine"
+#| echo: false
+#| warning: false
+#| message: false
 
-## Third discussion point
+# Get average rating per cuisine
+cuisine_summary <- data %>%
+  group_by(cuisine) %>%
+  summarize(num_restaurants = n(), avg_rating = mean(rating))
+
+# Plot number of restaurants vs average rating
+ggplot(cuisine_summary, aes(x = num_restaurants, y = avg_rating)) +
+  geom_point() +
+  geom_text(aes(label=cuisine), nudge_y = 0.02, size = 3, angle = 25) +
+  labs(x = "Number of Restaurants", y = "Average Rating") +
+  theme_minimal()
+```
+
+## Price Range and Rating
+
+We also observed that higher price range of a restaurant means the restaurant will higher ratings.
+We have expected this in the model section, but the diminishing returns of ratings as price increases was not expected.
+We can plot out the relationship between the price and the rating by cuisine to further illustrate this idea.
+@Fig-rating-price shows that the lower rating cuisines do have lower average prices.
+But there are cuisines, such as Caribbean or Vietnamese that has a high rating, yet with lower average prices.
+The figure shows that for some cuisines, their price range doesn't affect their ratings.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: fig-rating-price
+#| fig-cap: "Average Rating vs. Average Price by Cuisine"
+#| warning: false
+
+cuisine_summary <- data %>%
+  group_by(cuisine) %>%
+  summarize(avg_price = mean(as.numeric(factor(price), ordered = TRUE)),
+            avg_rating = mean(rating))
+
+# Plot
+ggplot(cuisine_summary, aes(x = avg_price, y = avg_rating, label = cuisine)) +
+  geom_point() +
+  geom_text(aes(label = cuisine), nudge_x = 0.05, nudge_y = 0.05, size = 3, angle = 45, hjust = 1) +  # Add text labels with a slight nudge and angle
+  labs(x = "Average Price", y = "Average Rating",) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+This could have possibly been caused by simply those with lower prices cannot afford decent service and food, but that still does not explain the low average rating of Italian and American restaurants which have higher costs yet near the same rating as Mexican and Chinese restaurants.
+Another way this could have been caused is because, again, people rate rarer cuisines higher than common ones.
+So perhaps in later studies, more research can be done with those rarity in mind.
 
@@
 
-Weaknesses and next steps should also be included.
+A weakness that we have observed is that there may not be enough variables in our model to correctly model the rating.
+We could have added more factors, such as how rare the cuisine is in the dataset, or the number of reviews.
+We might have enough information to perform post-stratification with the number of ratings for a restaurant, but that would require a reliable, bigger dataset on reviews of restaurants which we do not have access to.
+
+Another limitation could have been in how we clean our data.
+We selected businesses that had restaurant-related categories in Yelp, but there is likely to be many businesses which forgot to add the restaurant related categories on Yelp, or simply does not care.
+Therefore, filtering restaurants by categories is unreliable.
+
+The data itself is also a limitation.
+The data only contains restaurants from big cities, such as Toronto, Vancouver, and Las Vegas.
+This could have caused a skew in our dataset, over-representing restaurants in bigger cities, and not those in the smaller, suburban communities.
+Not only that, the ratings of restaurants were given in 0.5 increments which meant it isn't the most accurate rating we could have gotten.
+
+Next steps to take are refining this model to take account of different variables that were missed in this paper and improving the predictability of the model.
+Perhaps with a newer database, this study shall be repeated too.
 
@@
 # Appendix {.unnumbered}
+
+# Cleaned Dataset Interactive Map {#sec-dataset-map}
 
@@
 plot(model, "trace") +
+    theme_minimal() +
     theme(legend.position = "bottom")

### 2024-04-19 scripts/05-make_map.R

@@ -1,0 +1,81 @@
+#### Preamble ####
+# Purpose: Makes a Leaflet map which will show all the restaurants in the database
+# Author: Moohaeng Sohn
+# Date: 18 April 2024
+# Contact: alex.sohn@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Download libraries used, download Yelp Dataset (look at 01-download_data.R)
+
+#### Workspace setup ####
+library(tidyverse)
+library(jsonlite)
+library(leaflet)
+library(htmlwidgets)
+
+#### Clean data ####
+# Same steps as in 02-data_cleaning.R, except we keep longitude/latitudes
+# Load in data
+business <- stream_in(file("./data/raw_data/yelp_academic_dataset_business.json", 'r'))
+
+# Filter out non-restaurant businesses
+restaurant_categories <- c("Restaurants", "Bars", "Fast Food")
+
+business <- business |>
+  flatten(recursive = TRUE) |>
+  filter(grepl(paste(restaurant_categories, collapse = "|"), categories)) # turn restaurant categories as regex and match
+
+# Make a new column which indicate what cuisine type this restaurant is
+# This list of cuisine is based on the Yelp dataset's categories 
+cuisines <- c("American", "Mexican", "Italian", "Chinese", "Japanese", "Mediterranean", "Thai", "Vietnamese", "Indian", "Caribbean", "Middle Eastern", "French")
+cuisines_business <- business |>
+  # Filter out none category restaurants
+  filter(!is.na(attributes.RestaurantsPriceRange2), attributes.RestaurantsPriceRange2 != "None") |>
+  mutate(cuisine = case_when(
+    # If any of the cuisines in the category, categorize them as that cuisine
+    str_detect(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)) ~ 
+      str_extract(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)),
+    # If not, put them as Other
+    TRUE ~ "Other"
+  ),
+  price = as.numeric(attributes.RestaurantsPriceRange2)) |>
+  select(name, latitude, longitude, stars, cuisine, price)
+  
+#### Make map ####
+# Code from https://www.earthdatascience.org/courses/earth-analytics/get-data-using-apis/leaflet-r/
+# optimization option specified in:
[…]

### 2024-04-19 paper/paper.qmd
style files

@@
 
-We used the programming language R [@citeR], along with packages `tidyverse` [@tidyverse], `rstanarm` [@rstanarm], `jsonlite` [@jsonlite], `arrow` [@arrow], `modelsummary` [@modelsummary], `kableExtra` [@kableExtra], `here` [@here], `leaflet` [@leaflet], `htmlwidgets` [@htmlwidgets].
+We used the programming language R [@citeR], along with packages `tidyverse` [@tidyverse], `rstanarm` [@rstanarm], `jsonlite` [@jsonlite], `arrow` [@arrow], `modelsummary` [@modelsummary], `kableExtra` [@kableExtra], `here` [@here], `leaflet` [@leaflet], `htmlwidgets` [@htmlwidgets], and `styler` [@styler].
 
@@
   geom_histogram(binwidth = 0.25, fill = "grey", color = "black") +
-  labs(title = "Distribution of Star Ratings",
+  labs(
+    title = "Distribution of Star Ratings",
     x = "Stars",
-       y = "Frequency") +
+    y = "Frequency"
+  ) +
   theme_minimal()
@@
   geom_bar(stat = "identity") +
-  labs(x = "Cuisine",
+  labs(
+    x = "Cuisine",
     y = "Percentage",
-       fill = "Price Range") +
+    fill = "Price Range"
+  ) +
   theme_minimal() +
@@
   geom_point() +
-  geom_text(aes(label=cuisine), nudge_y = 0.02, size = 3, angle = 25) +
+  geom_text(aes(label = cuisine), nudge_y = 0.02, size = 3, angle = 25) +
   labs(x = "Number of Restaurants", y = "Average Rating") +
@@
   group_by(cuisine) %>%
-  summarize(avg_price = mean(as.numeric(factor(price), ordered = TRUE)),
-            avg_rating = mean(rating))
+  summarize(
+    avg_price = mean(as.numeric(factor(price), ordered = TRUE)),
+    avg_rating = mean(rating)
+  )
 
@@
   geom_text(aes(label = cuisine), nudge_x = 0.05, nudge_y = 0.05, size = 3, angle = 45, hjust = 1) + # Add text labels with a slight nudge and angle
-  labs(x = "Average Price", y = "Average Rating",) +
+  labs(x = "Average Price", y = "Average Rating", ) +
   theme_minimal() +
@@
 
+Be wary of lag, there are tens of thousands of datapoints being plotted, and it may lag on machines that are not fast.
+
+The raw dataset map is here: [https://alexsohn1126.github.io/yelp-analysis/other/map/rawmap.html](https://alexsohn1126.github.io/yelp-analysis/other/map/rawmap.html)
+
+As you can see, there are no datapoints near Toronto, Montreal, or Calgary like the documentation has stated.
+
+The cleaned dataset map here: [https://alexsohn1126.github.io/yelp-analysis/other/map/map.html](https://alexsohn1126.github.io/yelp-analysis/other/map/map.html)
+
+The datapoints are colored by their price ranges. Clicking on each datapoint will show it's name, rating, cuisine, and price.
+
 # Model details {#sec-model-details}
@@
 pp_plot
-
 ```
@@
   theme(legend.position = "bottom")
-
 ```

### 2024-04-19 scripts/00-simulate_data.R

@@ -17,7 +17,7 @@ set.seed(302)
 num_restaurants <- 10
 
 restaurants <- tibble(
-  # restaurant names will be "Restaurant 1", "Restaurant 2" and so on... 
+  # restaurant names will be "Restaurant 1", "Restaurant 2" and so on...
   restaurant_name = paste("Restaurant", seq(1:num_restaurants)),
   # Generating random float ratings between 1 and 5
   rating = runif(num_restaurants, min = 1, max = 5),
@@ -29,7 +29,7 @@ restaurants <- tibble(
 
 # Test column types
 is.character(restaurants$restaurant_name)
-is.numeric(restaurants$rating) 
+is.numeric(restaurants$rating)
 is.character(restaurants$cuisine)
 
 # Test rating bounds

### 2024-04-19 scripts/01-download_data.R

@@ -11,9 +11,7 @@
 # You must download the dataset manually.
 
 # Instrucitons (From this repo's README.md):
-# Visit https://www.yelp.com/dataset (Last accessed: 2024 April 15), then click "Download Dataset", 
-# fill out the personal information, and download the JSON (NOT the photos). 
-# Extract and place the files in `data/raw_data` folder (there should be `PLACE_EXTRACTED_YELP_DATASET_HERE` file there). 
+# Visit https://www.yelp.com/dataset (Last accessed: 2024 April 15), then click "Download Dataset",
+# fill out the personal information, and download the JSON (NOT the photos).
+# Extract and place the files in `data/raw_data` folder (there should be `PLACE_EXTRACTED_YELP_DATASET_HERE` file there).
 # There will be multiple JSONs, put all of them in `data/raw_data` folder.
-
-         

### 2024-04-19 scripts/02-data_cleaning.R

@@ -13,7 +13,7 @@ library(arrow)
 
 #### Clean data ####
 # Load in data
-business <- stream_in(file("./data/raw_data/yelp_academic_dataset_business.json", 'r'))
+business <- stream_in(file("./data/raw_data/yelp_academic_dataset_business.json", "r"))
 
 # Filter out non-restaurant businesses
 restaurant_categories <- c("Restaurants", "Bars", "Fast Food")
@@ -23,21 +23,22 @@ business <- business |>
   filter(grepl(paste(restaurant_categories, collapse = "|"), categories)) # turn restaurant categories as regex and match
 
 # Make a new column which indicate what cuisine type this restaurant is
-# This list of cuisine is based on the Yelp dataset's categories 
+# This list of cuisine is based on the Yelp dataset's categories
 cuisines <- c("American", "Mexican", "Italian", "Chinese", "Japanese", "Mediterranean", "Thai", "Vietnamese", "Indian", "Caribbean", "Middle Eastern", "French")
 cuisines_business <- business |>
   # Filter out none category restaurants
   filter(!is.na(attributes.RestaurantsPriceRange2), attributes.RestaurantsPriceRange2 != "None") |>
-  mutate(cuisine = case_when(
-    # If any of the cuisines in the category, categorize them as that cuisine
-    str_detect(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)) ~ 
-      str_extract(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)),
-    # If not, put them as Other
-    TRUE ~ "Other"
-  ),
-  price = as.numeric(attributes.RestaurantsPriceRange2)) |>
-  select(restaurant_name=name, rating=stars, cuisine, price)
+  mutate(
+    cuisine = case_when(
+      # If any of the cuisines in the category, categorize them as that cuisine
+      str_detect(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)) ~
+        str_extract(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)),
+      # If not, put them as Other
+      TRUE ~ "Other"
+    ),
+    price = as.numeric(attributes.RestaurantsPriceRange2)
+  ) |>
+  select(restaurant_name = name, rating = stars, cuisine, price)
 
 #### Save data ####
 write_parquet(cuisines_business, "./data/analysis_data/restaurant_data.parquet")
-

### 2024-04-19 scripts/03-test_data.R

@@ -17,7 +17,7 @@ restaurants <- read_parquet("./data/analysis_data/restaurant_data.parquet")
 #### Test data ####
 # Test column types
 is.character(restaurants$restaurant_name)
-is.numeric(restaurants$rating) 
+is.numeric(restaurants$rating)
 is.character(restaurants$cuisine)
 
 # Test rating bounds
@@ -28,4 +28,3 @@ all(restaurants$rating <= 5)
 # Test that categories are types of cuisines that we specified
 cuisines <- c("American", "Mexican", "Italian", "Chinese", "Japanese", "Mediterranean", "Thai", "Vietnamese", "Indian", "Caribbean", "Middle Eastern", "French", "Other")
 all(is.element(restaurants$cuisine, cuisines))
-

### 2024-04-19 scripts/04-model.R

@@ -19,7 +19,7 @@ data <- read_parquet("./data/analysis_data/restaurant_data.parquet")
 
 # Rough model
 # Don't import the whole MASS library as it interferes with select() from tidyverse
-#rough_model <-
+# rough_model <-
 #  MASS::polr(factor(rating) ~ cuisine + factor(price), data = data)
 
 # uses 6 cores, reduce if necessary
@@ -37,5 +37,3 @@ saveRDS(
   model,
   file = "models/restaurant_rating_model_ord_logit.rds"
 )
-
-

### 2024-04-19 scripts/05-make_map.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Makes a Leaflet map which will show all the restaurants in the database
 # Author: Moohaeng Sohn
-# Date: 18 April 2024
+# Date: 19 April 2024
 # Contact: alex.sohn@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Download libraries used, download Yelp Dataset (look at 01-download_data.R)
@@ -15,7 +15,7 @@ library(htmlwidgets)
 #### Clean data ####
 # Same steps as in 02-data_cleaning.R, except we keep longitude/latitudes
 # Load in data
-business <- stream_in(file("./data/raw_data/yelp_academic_dataset_business.json", 'r'))
+business <- stream_in(file("./data/raw_data/yelp_academic_dataset_business.json", "r"))
 
 # Filter out non-restaurant businesses
 restaurant_categories <- c("Restaurants", "Bars", "Fast Food")
@@ -25,57 +25,68 @@ business <- business |>
   filter(grepl(paste(restaurant_categories, collapse = "|"), categories)) # turn restaurant categories as regex and match
 
 # Make a new column which indicate what cuisine type this restaurant is
-# This list of cuisine is based on the Yelp dataset's categories 
+# This list of cuisine is based on the Yelp dataset's categories
 cuisines <- c("American", "Mexican", "Italian", "Chinese", "Japanese", "Mediterranean", "Thai", "Vietnamese", "Indian", "Caribbean", "Middle Eastern", "French")
 cuisines_business <- business |>
   # Filter out none category restaurants
   filter(!is.na(attributes.RestaurantsPriceRange2), attributes.RestaurantsPriceRange2 != "None") |>
-  mutate(cuisine = case_when(
-    # If any of the cuisines in the category, categorize them as that cuisine
-    str_detect(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)) ~ 
-      str_extract(categories, regex(paste(cuisines, collapse = "|"), ignore_case = TRUE)),
-    # If not, put them as Other
-    TRUE ~ "Other"
-  ),
-  price = as.numeric(attributes.RestaurantsPriceRange2)) |>
+  mutate(
+    cuisine = case_when(
+      # If any of the cuisines in the category, categorize them as that cuisine
[…]

### 2024-04-19 paper/paper.qmd
Reflect title change in the paper

@@
 ---
-title: "Modelling the Yelp Rating of Restaurants: Disparity of Rating Between Restaurant Cuisines and Prices"
+title: "Modelling the Yelp Rating of Restaurants: Disparity of Rating Between Different Restaurant Cuisines and Prices"
 author: 
